### 2022-05-23 sections/bdt_Htautau.tex
minor update to V1.5

receive operating characteristic (ROC) score drops more than 2\%.

@@

\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in eq.~(\ref{eq:eq1}).

@@

\item \text{min}($m_{\text{jj}}$) is the minimum value of all the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.

>>>>

received operating characteristic (ROC) score drops more than 2\%.

@@

\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in Eq.~(\ref{eq:eq1}).

@@

\item \text{min}($m_{\text{jj}}$) is the minimum value of the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.

### 2022-05-23 sections/data_presel.tex
minor update to V1.5

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay. Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}

>>>>

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay. Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the final states of other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}
